Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-15 paper/main.tex
notes from thursday + some changes

The inclusion maps $iota$ can be used to piece together the subsets $U_{i}$, particularly individual points $\dbasepoint \in \dbase$. This is how we provide knowledge of continuity to the artist \vartist\ in a way where the artist does not need all the data at once. This is what allows the artist to generate graphics where the subset of data on view is dynamically updated, such as pan and zoom navigation\cite{NekrasovskiEvaluationPanZoom2006} and sliding windows on streaming data\cite{crouchDynamicGraphsSlidingwindow2013,chuTimeSeriesSegmentation1995}.

@@

\begin{definition} The category $\textcolor{section}{\mathcal{T}}$ consists of 
  \label{def:category:Tau}
  \begin{itemize}
  \item \textit{object} the set of sections $\Gamma(U_i)$ where $U_i$ can be any open set object in $\mathcal{\dbase}$
  \item \textit{morphisms} fiber maps $Hom(F, F)$, because sections are maps from a point in the base space to a point in the fiber $\tau: \dbase \rightarrow \dfiber$
  \end{itemize}
\end{definition}

>>>>

The inclusion maps $\iota$ can be used to piece together the subsets $U_{i}$, particularly individual points $\dbasepoint \in \dbase$. This is how we provide knowledge of continuity to the artist \vartist\ in a way where the artist does not need all the data at once. This is what allows the artist to generate graphics where the subset of data on view is dynamically updated, such as pan and zoom navigation\cite{NekrasovskiEvaluationPanZoom2006} and sliding windows on streaming data\cite{crouchDynamicGraphsSlidingwindow2013,chuTimeSeriesSegmentation1995}.

@@

\begin{definition} The category $\textcolor{section}{\mathcal{T}}$ consists of 
  \label{def:category:Tau}
  \begin{itemize}
  \item \textit{object} the set of sections $\Gamma(U, \dtotal)$ where $U$ can be any object in $\mathcal{\dbase}$
  \item \textit{morphisms} restrictions \note{\iota which we will use in (6) so 7 is cleanly abstracted}
  \end{itemize}
\end{definition}
